Testing Quasar Unification with Clumpy Wind Models

### 2015-11-10 paper.tex
updated figure

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec.png}
\caption
{
Synthetic spectra at five viewing angles in our model. The coloured lines
show different quasar and BAL quasar composites, and the dotted line shows a disc
only continuum to show the effect of the outflow on the continuum level.  
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

The model produces strong emission lines in \civ, \nv\ and \la,
as well as a weak \mg\ line. The shapes and widths of these lines
match the composites fairly well. However, the line-to-continuum ratios 
at low inclinations in our model are significantly weaker than the quasar 
composites. Increasing the density of the outflow, by altering the mass 
loss rate  or velocity law, can produce more line emission.
However, the red wing of the BAL profiles is generally stronger than 
seen in BALQSO spectra and composites. This illustrates a fundamental 
problem with a geometric unification model such as this:
that the line-to-continuum ratios at low inclinations are
significantly affected by disc foreshortening and limb darkening.
The angular distribution of the disc radiation is clearly
crucially important in determining the emergent line ratios.

@@

BALQSOs and quasars generally possess very similar emission line properties 
\citep[e.g.][]{weymann1991,reichard2003}. To demonstrate this, we show equivalent width
mean values and standard devaitions from REF in table 3. Clearly, the variation
with inclination in our models is far greater than than the variation 
between, and standard deviation within, quasar and BALQSO samples.  
This presents a challenge to our model, as well as the geometric unification picture in general.
One obvious potential solution to this problem is to hypothesize a more isotropic distribution 
for the emergent condition than predicted by a classical thin disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
However, we have verified using AGNSPEC (REFs to Hubeny)
that this effect is small in the UV and optical wavelength regimes, 
and the disc is still anisotropic.

>>>>

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
\caption
{
Synthetic spectra at five viewing angles in our model. The coloured lines
show different quasar and BAL quasar composites, and the dotted line shows a disc
only continuum to show the effect of the outflow on the continuum level.  
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

The model produces strong emission lines in \civ, \nv\ and \la,
as well as a weak \mg\ line. The shapes and widths of these lines
match the composites fairly well. However, the line-to-continuum ratios 
at low inclinations in our model are significantly weaker than the quasar 
composites. Increasing the density of the outflow, by altering the mass 
loss rate  or velocity law, can produce more line emission.
However, the red wing of the BAL profiles is generally stronger than 
seen in BALQSO spectra and composites. This illustrates a fundamental 
problem with a geometric unification model such as this:
that the line-to-continuum ratios at hight inclinations are
significantly affected by disc foreshortening and limb darkening.
The angular distribution of the disc radiation is clearly
crucially important in determining the emergent line ratios.

@@

BALQSOs and quasars generally possess very similar emission line properties 
\citep[e.g.][]{weymann1991,reichard2003}. 
Clearly, the variation with inclination in our models is far greater than 
than the variation between, and standard deviation within, quasar and BALQSO samples.  
This presents a challenge to our model, as well as the geometric unification picture in general.
One obvious potential solution is to hypothesize a more isotropic distribution 
for the emergent condition than predicted by a classical thin disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
However, we have verified using AGNSPEC (REFs to Hubeny)
that this effect is small in the UV and optical wavelength regimes, 
and the disc is still anisotropic.
